### 2023-11-07 Notes/optest_update.tex
Updated description of estimators in update.

>>>>

I wanted to give a brief comment on the origin of each of these estimators. The 
first estimator $\hat \theta_{prop}$ is the estimator proposed by Dr. Kim. The 
original goal was to show that this is optimal. The second estimator, 
$\hat \theta^{ind}_{prop}$ is the first estimator with different functions of 
$\delta$ to try to make each component more independent from each other. The 
problem with this is that the components are still dependent and it has worse 
properties in simulation studies (next section). The estimator $\hat \theta_c$ 
is the originial estimator $\hat \theta_{prop}$ with different coefficients that
hopefully make it slightly more efficient. The estimator $\hat \theta_{c, ind}$ 
does the same thing with $\hat \theta_{prop}^{ind}$. Finally, 
$\hat \theta_{\delta}$ uses the functional form of Theorem 7.2 from 
\cite{tsiatis2006semiparametric} and optimized coefficients.
